---
title: "Introduction to dpurifyr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to dpurifyr}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
```{r, cache=FALSE}
knitr::opts_chunk$set(error = TRUE, warning = FALSE)
```
This document introduces you to dpurifyr’s basic set of tools, and shows you how to apply them to data frames. 
At first, we load the libraries which we use in this vignettes.

```{r, message=FALSE}
library("tidyverse")
library("titanic")
library("xgboost")
library("dpurifyr")
```

## Data: titanic

To explore the basic data manipulation verbs of dpurifyr, we’ll use titanic data set from `titanic` package. 

This dataset contains data of the real Titanic passengers. 
Each row represents one person. 
The columns describe different attributes about the person including whether they survived (Survived), their age (Age), 
their sex (Sex) and so on.
```{r}
df <- titanic::titanic_train
head(df)
```

In this vignettes, we use specific columns and select these using `dplyr::select()` :
```{r}
df <- dplyr::select(df, Survived, Pclass, Sex, Age, SibSp, Parch, Fare)
```

After that, we split `df` in to train, test data.
```{r}
# 70% data are training data
index <- sample(seq_len(nrow(df)), 0.7*nrow(df))
df_train <- df[index, ]
df_test <- df[-index, ]
```

Here, we simply replace `NA` with its mean values using `tidy::replace_na()`.
```{r}
df_train <- replace_na(df_train, list(Age=mean(df_train$Age, na.rm=TRUE)))
df_test <- replace_na(df_test,list(Age=mean(df_test$Age, na.rm=TRUE)))
```

## Simple usage of dpurifyr
`glm()` is used to fit generalized linear models.
It allows us to use a symbolic description of the linear predictor.
```{r}
lgt <- glm(Survived ~ ., data=df_train, family=binomial(link="logit"))
```


```{r}
#Prepare data
x <- dplyr::select(df_train, -Survived)
y <- dplyr::select(df_train,  Survived)
```

But, `xgboost` which is the algorithm that wins every competition does not.
```{r eval=FALSE}
xgboost(data=x, label=y, objective = "binary:logistic")
```
```
Error in xgb.get.DMatrix(data, label, missing, weight) : 
  xgboost only support numerical matrix input,
           use 'data.matrix' to transform the data.
In addition: Warning message:
In xgb.get.DMatrix(data, label, missing, weight) :
  xgboost: label will be ignored.
```

This is caused by the limitation of `xgboost` library which does not allow to use `factor`, `string`.
In this case, we can utilize `dpurifyr` package.
`dpurifyr` offers a lot of preprocessing functions.
You can convert original data `x` into matrix form data `x_data` using `dpurifyr` package.
```{r}
x_train <- x %>% 
  dpurifyr::encode_label(Sex) %>% 
  dpurifyr::encode_onehot(Pclass) %>%
  dpurifyr::to_matrix()
y_train <- dpurifyr::to_vector(y)
```

As a result, you can put data into `xgboost()`:
```{r}
bst <- xgboost(data=x_train, label=y_train, nrounds=2, objective="binary:logistic")
bst
```

## Using the same preprocessing with train data to test data
After preprocessing, you get `x_train` object in the previous section.
`dpurifyr::apply()` allows users to do the same preprocessing with `x_train` to the other data (here, `x_test`):
```{r}
# Create x_test object like x_train
x_test <- dplyr::select(df_test, -Survived) %>%
  dpurifyr::apply(x_train)
# Create y_test like _train
y_test <- unlist(dplyr::select(df_test,  Survived))
```

```{r}
bst <- xgboost(data=x_test, label=y_test, nrounds=2, objective="binary:logistic")
```
